Paper Figures and Text

### 2024-03-12 Fish Data Analysis/Paper_Figures.qmd
Trial Single Fish

```{r}
fish_comp_data <- read.csv("Data/Fish_Comp_Values_3D.csv") %>%
                           mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                           mutate(Ablation = ifelse(Ablation  == "N", "No Ablation", "Ablated")) %>%
                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
                           separate(Fish, c("Fish1", "Fish2"),sep="x") %>%

@@

@@

nn_heading_sum_close <- fish_data_nn_normal_close %>% mutate(angle_bins = round_any(Angle,pi/6)) %>%
                                                group_by(angle_bins,Flow,Ablation,Darkness,Flow_Ablation_Darkness) %>%
                                                summarise(mean_turn = mean(Fish1_Yaw_Heading_PS, na.rm = T),
                                                          sd_turn = sd(Fish1_Yaw_Heading_PS, na.rm = T),
                                                          n = n()) %>%
                                                ungroup() %>%
                                                na.omit()

@@

nn_heading_sum_far <- fish_data_nn_normal_far %>% mutate(angle_bins = round_any(Angle,pi/6)) %>%
                                                group_by(angle_bins,Flow,Ablation,Darkness,Flow_Ablation_Darkness) %>%
                                                summarise(mean_turn = mean(Fish1_Yaw_Heading_PS, na.rm = T),
                                                          sd_turn = sd(Fish1_Yaw_Heading_PS, na.rm = T),
                                                          n = n()) %>%
                                                ungroup() %>%
                                                na.omit()
```

@@

heading_PS_model_close <- lmer(Fish1_Yaw_Heading_PS ~ 0 + sin(Angle) + sin(Angle):Ablation + sin(Angle):Darkness + sin(Angle):Ablation:Darkness + (1|Date), 
                   data = fish_data_nn_normal_close %>% filter(Flow == "Still Water")) 
Anova(heading_PS_model_close)

heading_PS_model_far <- lmer(Fish1_Yaw_Heading_PS ~ 0 + sin(Angle) + sin(Angle):Ablation + sin(Angle):Darkness + sin(Angle):Ablation:Darkness + (1|Date), 
                   data = fish_data_nn_normal_far %>% filter(Flow == "Still Water")) 
Anova(heading_PS_model_far)

heading_PS_graph_close <- ggplot(nn_heading_sum_close %>% filter(Flow == "Still Water"),
       aes(x = angle_bins, y = rad2deg(mean_turn), color = interaction(Ablation, Darkness, sep =", ")))+
  geom_point()+
  geom_line(aes(y = rad2deg(predict(heading_PS_model_close,
                    newdata = nn_heading_sum_close %>% filter(Flow == "Still Water") %>% mutate(Angle = angle_bins),
                    re.form = NA))), size = 1)+
  theme_classic() +
  ylim(-75,75) +
  xlab("Direction of Neighbour (Degrees)") +
  ylab("Focal Fish Turning Angle Speed (Degrees/Sec)") +
  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
  scale_x_continuous(breaks = unique(nn_heading_sum_close$angle_bins),
                     labels = rad2deg(unique(nn_heading_sum_close$angle_bins))) +
  labs(color = "Sensory Conditions")

heading_PS_graph_far <- ggplot(nn_heading_sum_far %>% filter(Flow == "Still Water"),
       aes(x = angle_bins, y = rad2deg(mean_turn), color = interaction(Ablation, Darkness, sep =", ")))+
  geom_point()+
  geom_line(aes(y = rad2deg(predict(heading_PS_model_far,
                    newdata = nn_heading_sum_far %>% filter(Flow == "Still Water") %>% mutate(Angle = angle_bins),
                    re.form = NA))), size = 1)+
  theme_classic() +
  ylim(-75,75) +
  xlab("Direction of Neighbour (Degrees)") +
  ylab("Focal Fish Turning Angle Speed (Degrees/Sec)") +
  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
  scale_x_continuous(breaks = unique(nn_heading_sum_far$angle_bins),
                     labels = rad2deg(unique(nn_heading_sum_far$angle_bins))) +
  labs(color = "Sensory Conditions")

@@

>>>>

```{r}
fish_comp_data <- read.csv("Data/Fish_Comp_Values_3D.csv") %>%
                           mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                           mutate(Ablation = ifelse(Ablation  == "N", "No Ablation", "Ablated")) %>%
                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
                           separate(Fish, c("Fish1", "Fish2"),sep="x") %>% 
                           mutate(Type = "Eight") %>%

@@

fish_comp_data_single <- read.csv("Data/Fish_Comp_Values_3D_Single.csv") %>%
                           mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                           mutate(Ablation = ifelse(Ablation  == "S", "No Ablation")) %>%
                           mutate(Darkness = ifelse(Darkness == "S", "Light")) %>%
                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Flow = fct_relevel(Flow, c("Still Water"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation"))) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Light"))) %>%
                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
                           separate(Fish, c("Fish1", "Fish2"),sep="x") %>% 
                           mutate(Type = "Single") %>%

fish_comp_data_single <- na.omit(fish_comp_data_single)

fish_comp_data <- rbind(fish_comp_data,fish_comp_data_single)

@@

nn_heading_sum_close <- fish_data_nn_normal_close %>% mutate(angle_bins = round_any(Angle,pi/6)) %>%
                                                group_by(angle_bins,Flow,Ablation,Darkness,Type,Flow_Ablation_Darkness) %>%
                                                summarise(mean_turn = mean(Fish1_Yaw_Heading_PS, na.rm = T),
                                                          sd_turn = sd(Fish1_Yaw_Heading_PS, na.rm = T),
                                                          n = n()) %>%
                                                ungroup() %>%
                                                na.omit()

@@

nn_heading_sum_far <- fish_data_nn_normal_far %>% mutate(angle_bins = round_any(Angle,pi/6)) %>%
                                                group_by(angle_bins,Flow,Ablation,Darkness,Type,Flow_Ablation_Darkness) %>%
                                                summarise(mean_turn = mean(Fish1_Yaw_Heading_PS, na.rm = T),
                                                          sd_turn = sd(Fish1_Yaw_Heading_PS, na.rm = T),
                                                          n = n()) %>%
                                                ungroup() %>%
                                                na.omit()
```

@@

heading_PS_model_close <- lmer(Fish1_Yaw_Heading_PS ~ 0 + sin(Angle) + sin(Angle):Type + sin(Angle):Ablation + sin(Angle):Darkness + sin(Angle):Ablation:Darkness + (1|Date), 
                   data = fish_data_nn_normal_close %>% filter(Flow == "Still Water")) 
Anova(heading_PS_model_close)

heading_PS_model_far <- lmer(Fish1_Yaw_Heading_PS ~ 0 + sin(Angle) + sin(Angle):Type + sin(Angle):Ablation + sin(Angle):Darkness + sin(Angle):Ablation:Darkness + (1|Date), 
                   data = fish_data_nn_normal_far %>% filter(Flow == "Still Water")) 
Anova(heading_PS_model_far)

heading_PS_graph_close <- ggplot(nn_heading_sum_close %>% filter(Flow == "Still Water"),
       aes(x = angle_bins, y = rad2deg(mean_turn), color = interaction(Ablation, Darkness, sep =", ", line = Type)))+
  geom_point(size = 3)+
  geom_line(aes(y = rad2deg(predict(heading_PS_model_close,
                    newdata = nn_heading_sum_close %>% filter(Flow == "Still Water") %>% mutate(Angle = angle_bins),
                    re.form = NA))), size = 2)+
  theme_classic() +
  ylim(-75,75) +
  xlab("Direction of Neighbour (Degrees)") +
  ylab("Focal Fish Turning Angle Speed (Degrees/Sec)") +
  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color,"red")) +
  scale_x_continuous(breaks = unique(nn_heading_sum_close$angle_bins),
                     labels = rad2deg(unique(nn_heading_sum_close$angle_bins))) +
  labs(color = "Sensory Conditions")+
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))

heading_PS_graph_far <- ggplot(nn_heading_sum_far %>% filter(Flow == "Still Water"),
       aes(x = angle_bins, y = rad2deg(mean_turn), color = interaction(Ablation, Darkness, sep =", ")))+
  geom_point(size = 3)+
  geom_line(aes(y = rad2deg(predict(heading_PS_model_far,
                    newdata = nn_heading_sum_far %>% filter(Flow == "Still Water") %>% mutate(Angle = angle_bins),
                    re.form = NA))), size = 2)+
  theme_classic() +
  ylim(-75,75) +
  xlab("Direction of Neighbour (Degrees)") +
  ylab("Focal Fish Turning Angle Speed (Degrees/Sec)") +
  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color,"red")) +
  scale_x_continuous(breaks = unique(nn_heading_sum_far$angle_bins),
                     labels = rad2deg(unique(nn_heading_sum_far$angle_bins))) +
  labs(color = "Sensory Conditions")+
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))

@@

test(emmeans(heading_PS_model_far, pairwise ~Ablation*Darkness*Type | Angle, at = list(Angle = c(pi/2))))
